Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-23 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
Minor
Tex stuff

\author{Gabriel Riutort-Mayol \and Paul-Christian Bürkner \and Michael R.\ Andersen \and Arno Solin \and Aki Vehtari
}

@@

An upper bounded approximation to the coefficients $\tilde{q}_j^2$ and $\tilde{q}_0^2$ can be obtained by taking the limit $J \rightarrow \infty$ in the sub-sums in the corresponding equations (\ref{eq_q}) and (\ref{eq_q0}), and thus leading to the following variance coefficients:
%
\begin{equation}\label{eq_q_2}
\begin{split}
\tilde{q}_j^2=& \frac{2\mathrm{I}_j(\ell^{-2})}{\exp(\frac{1}{\ell^2})}, \\
\tilde{q}_0^2=& \frac{\mathrm{I}_0(\ell^{-2})}{\exp(\frac{1}{\ell^2})},
\end{split}
\end{equation} 
for $j=1,2,\cdots,J$, and where the $\mathrm{I}_{j}(z)$ is the modified Bessel function \citep{handbook1970m} of the first kind. This approximation implies that the requirement of a valid covariance function is relaxed and only an optimal series approximation is required. A more detailed explanation and mathematical proofs of this approximation of a periodic covariance function are provided by \citet{solin2014explicit}.

>>>>

\author{Gabriel Riutort-Mayol \and Paul-Christian Bürkner \and Michael R.\ Andersen \and Arno~Solin \and Aki Vehtari
}

@@

An upper bounded approximation to the coefficients $\tilde{q}_j^2$ and $\tilde{q}_0^2$ can be obtained by taking the limit $J \rightarrow \infty$ in the sub-sums in the corresponding equations (\ref{eq_q}) and (\ref{eq_q0}), and thus leading to the following variance coefficients:
%
\begin{equation}\label{eq_q_2}
\begin{split}
\tilde{q}_j^2=& \frac{2\mathrm{I}_j(\ell^{-2})}{\exp(\frac{1}{\ell^2})}, \\
\tilde{q}_0^2=& \frac{\mathrm{I}_0(\ell^{-2})}{\exp(\frac{1}{\ell^2})},
\end{split}
\end{equation} 
for $j=1,2,\ldots,J$, and where the $\mathrm{I}_{j}(z)$ is the modified Bessel function \citep{handbook1970m} of the first kind. This approximation implies that the requirement of a valid covariance function is relaxed and only an optimal series approximation is required. A more detailed explanation and mathematical proofs of this approximation of a periodic covariance function are provided by \citet{solin2014explicit}.
